An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-05-15 paper.tex
Fix typo: L2 cache lockdown

    \begin{table*}[]
        \centering \caption{Experiment Platforms}
        \label{hardware_list}
	\begin{tabular}{|l|c|c|} \hline Platform Name & Altera
        Cyclone V Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
        \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache
        locked down to CPU1,\\ Isolated CPU1,\\ Enabled tickless on CPU1 \\ Real-time task pinned to CPU1 \end{tabular}
    \\ \hline \end{tabular} \end{table*}

>>>>

    \begin{table*}[]
        \centering \caption{Experiment Platforms}
        \label{hardware_list}
	\begin{tabular}{|l|c|c|} \hline Platform Name & Altera
        Cyclone V Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
        \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache lockdown on isolated CPU1,\\ Enabled tickless on CPU1 \\ Real-time task pinned to CPU1 \end{tabular}
    \\ \hline \end{tabular} \end{table*}
